The zoon R package for reproducible and shareable species distribution modelling

### 2017-01-31 ms.Rmd
unpack reproducibility

The zoon R package has been developed specifically to improve reproducibility and comparability of SDMs in R by allowing users to encode entire SDM analyses as reproducible workflows of independently executable, community-contributed modules.
The module-workflow structure enables scientists to more easily create and share components of their analysis; and then access, modify, reuse and combine the components of others (see below and Figure 1).
Whilst zoon's modular nature is similar to other SDM R packages such as BioMod2 [@Thuiller2009] and sdm [@Naimi2016], zoon instead pulls each module from an open repository that any SDM user can contribute to, and makes it easy for non-developers to contribute modules.
zoon's focus on reproducibile and modifiable workflows is inspired by repositories such as the Cardiac Web Lab [@Cooper2016] and workflow systems such as Taverna [@Wolstencroft2013a] and the BIOVEL system [@DeGiovanni2015; @DeGiovanni2016], but embeds an SDM-specific workflow system within R, making it much more accessible to the SDM community.

>>>>

The zoon R package has been developed specifically to improve reproducibility and comparability of SDMs in R by allowing users to encode entire SDM analyses as repeatable and extensible workflows consisting of independently executable, community-contributed modules.
The module-workflow structure enables scientists to more easily create and share components of their analysis; and then access, modify, reuse and combine the components of others (see below and Figure 1).
Whilst zoon's modular nature is similar to other SDM R packages such as BioMod2 [@Thuiller2009] and sdm [@Naimi2016], zoon instead pulls each module from an open repository that any SDM user can contribute to, and makes it easy for non-developers to contribute modules.
zoon's focus on reproducibile and modifiable workflows is inspired by repositories such as the Cardiac Web Lab [@Cooper2016] and workflow systems such as Taverna [@Wolstencroft2013a] and the BIOVEL system [@DeGiovanni2015; @DeGiovanni2016], but embeds an SDM-specific workflow system within R, making it much more accessible to the SDM community.
